A brief review of Quantum Mechanics for Computer Scientists

### 2023-06-18 documentation/article02/text/article.tex
New qubits representation added

		\par It's important to note that in Figure \ref{fig:qubitplot} and Equation \ref{eq:qubit}, a quantum state is often in a superposition because $\alpha$ and $\beta$ can take on multiple values along the bases axis. For example, if $\alpha = 1$ and $\beta = 0$, the qubit has a $100\%$ probability of being a 0 and $0\%$ probability of being a 1. Conversely, if $\alpha = \frac{1}{\sqrt{2}}$ and $\beta = \frac{1}{\sqrt{2}}$, there is a $50\%$ probability of being 1 and a $50\%$ of being 0.
		\newline

@@

			\par The \textbf{CNOT gate} in Equation \ref{eq:cnot} creates an \textbf{entanglement} between two qubits as shown in Equation \ref{eq:cnotApplyed}.
			\begin{equation}
				\label{eq:cnot}
				CNOT : 
				\begin{bmatrix}
					1& 0& 0& 0 \\
					0& 1& 0& 0 \\
					0& 0& 0& 1 \\
					0& 0& 1& 0
				\end{bmatrix}
			\end{equation}

>>>>

		\par It's important to note that in Figure \ref{fig:qubitplot} and Equation \ref{eq:qubit}, a quantum state is often in a superposition because $\alpha$ and $\beta$ can take on multiple values along the bases axis. For example, if $\alpha = 1$ and $\beta = 0$, the qubit has a $100\%$ probability of being a 0 and $0\%$ probability of being a 1. Conversely, if $\alpha = \frac{1}{\sqrt{2}}$ and $\beta = \frac{1}{\sqrt{2}}$, there is a $50\%$ probability of being 1 and a $50\%$ of being 0.\newline

		\par One good example of what a qubit can be is a photon. This particle has electric and magnetic components, forming an electric-magnetic field. We can interpret, for instance, the "vertical" component as the state 0 and the "horizontal" component as the state 1, as depicted in Figure \ref{fig:photonstate01}.

		\begin{figure}[h]
			\centering
			\includegraphics[width=0.7\linewidth]{images/photonState01}
			\caption[Qubit state]{Qubit state: $\alpha$ is the probability of this qubit collapsing to 0, and $\beta$ is the probability of this qubit collapsing to 1.}
			\label{fig:photonstate01}
		\end{figure}

		\par Note that in Figure \ref{fig:photonstate01}, there is a \textbf{superposition} of states, meaning that both 0 and 1 values can be assumed when the qubit is measured.

		\begin{figure}[h]
			\centering
			\includegraphics[width=0.7\linewidth]{images/photonState02}
			\caption[Qubit state 2]{Qubit state: $\alpha$ is the probability of this qubit collapsing to 0, and $\beta$ is the probability of this qubit collapsing to 1.}
			\label{fig:photonstate02}
		\end{figure}

		\par Note that in Figure \ref{fig:photonstate02}, there is also a \textbf{superposition}, but here the qubit is more likely to collapse to 0 because of a larger $\alpha$.

		\begin{figure}[h]
			\centering
			\includegraphics[width=0.7\linewidth]{images/photonState03}
			\caption[Qubit state 3]{Qubit state: $\alpha$ is the probability of this qubit collapsing to 0, and $\beta$ is the probability of this qubit collapsing to 1.}
			\label{fig:photonstate03}
		\end{figure}

		\par Again in Figure \ref{fig:photonstate03}, there is a \textbf{superposition}, but note that here the qubit is more likely to collapse to 1 because of a larger $\beta$.\newline

@@

			\par The \textbf{conditional not gate}(CNOT) in Equation \ref{eq:cnot} creates an \textbf{entanglement} between two qubits as shown in Equation \ref{eq:cnotApplyed}.
			\begin{equation}
				\label{eq:cnot}
				CNOT : 
				\begin{bmatrix}
					1& 0& 0& 0 \\
					0& 1& 0& 0 \\
					0& 0& 0& 1 \\
					0& 0& 1& 0
				\end{bmatrix}
			\end{equation}
